### 2022-03-02 paper/localpsf.tex
writing

Each point source $\delta_{x_i}$ in the Dirac comb is scaled by $1/V(x_i)$ so that the resulting scaled impulse responses within $\eta_k$ are comparable in magnitude. Note that we are not in danger of dividing by zero here, because our ellipsoid packing procedure from Section SEC excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold. Without this scaling, the portion of $\phi_{x_i}$ outside of $E_{x_i}$, which we neglect, could overwhelm $\phi_{x_j}$ for a nearby point $x_j$ simply because $V(x_i)$ is much larger than $V(x_j)$.

>>>>

Each point source $\delta_{x_i}$ in the Dirac comb is scaled by $1/V(x_i)$ so that the resulting scaled impulse responses within $\eta_k$ are comparable in magnitude. Note that we are not in danger of dividing by zero here, because our ellipsoid packing procedure from Section SEC excludes $x_i$ from consideration as a sample point if $V(x_i)$ is smaller than a predetermined threshold. Without this scaling, the portion of $\phi_{x_i}$ outside of $E_{x_i}$, which we neglect, will overwhelm $\phi_{x_j}$ for a nearby point $x_j$ if $V(x_i)$ is much larger than $V(x_j)$.
